DeepPicar: A Low-cost Deep Neural Network-based Autonomous Car

### 2018-01-26 paper/appendix.tex
Update conclusion and appendix

\begin{figure*}[t]
  \centering
  \includegraphics[width=.9\textwidth]{figs/TrainingLoss}
  \caption{Change in loss value throughout training.}
  \label{fig:modelloss}
\end{figure*}

@@

In the first method, we trained the neural network model across a set 
of 30 completed runs on the track seen in Figure~\ref{fig:track} by a
human pilot. Half of the runs saw the car driving one way along the
track, while the remaining half were of the car driving in the
opposite direction on the track.
In total, we collected 2,556 frames for training and 2,609 
frames for validation.
The weights of the network are initialized using a Xavier
initializer~\cite{Glorot2010}, which is known to provide better
initial values than the random weight assignment method.
In each training step, we use a batch
size of 100 frames, which are randomly selected among all the
collected training images, to optimize the network.
We repeat this across 2,000 training steps. When a model was trained
with the  aformentioned data, the training loss was 0.0188 and the
validation  loss was 0.0132.
The change of the loss value over the course of model training can be
seen in Figure~\ref{fig:modelloss}.

In the second method, we use the same data and parameters as  above 
except that now images are labeled as 'curved' and 'straight' and we pick an
equal number of images from each category at each training step to
update the model. In other words, we try to remove bias in selecting
images. We find that the car performed better in practice by applying
this approach as the car displayed a greater ability to stay in the
center of the track (on the white tape).
However, we find that there is a huge discrepency between the training
loss and the validation loss as the former was 0.009, while the latter
was 0.0869---a 10X difference---indicating that the model suffers from
an overfitting problem.

>>>>

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=1.1\textwidth, height=5cm]{figs/TrainingLoss}
  \caption{Change in loss value throughout training.}
  \label{fig:modelloss}
\end{figure}

In the first method, we trained the neural network model across a set 
of 30 completed runs on the track seen in Figure~\ref{fig:track} by a
human pilot. Half of the runs saw the car driving one way along the
track, while the remaining half were of the car driving in the
opposite direction on the track.
In total, we collected 2,481 frames for training and 2,534 
frames for validation.
The weights of the network are initialized using a Xavier
initializer~\cite{Glorot2010}, which is known to provide better
initial values than the random weight assignment method.
In each training step, we use a batch
size of 100 frames, which are randomly selected among all the
collected training images, to optimize the network.
We repeat this across 2,000 training steps. When a model was trained
with the  aformentioned data, the training loss was 0.0151 and the
validation  loss was 0.0251.
The change of the loss value over the course of model training can be
seen in Figure~\ref{fig:modelloss}.

In the second method, we use the same data and parameters as  above 
except that now images are labeled as 'curved' and 'straight' and we pick an
equal number of images from each category at each training step to
update the model. In other words, we try to remove bias in selecting
images. We find that the car performed better in practice by applying
this approach as the car displayed a greater ability to stay in the
center of the track (on the white tape).
However, we find that there is a huge discrepency between the training
loss and the validation loss as the former was 0.0126, while the latter
was 0.0725 --- almost a 6X difference---indicating that the model 
suffers from an overfitting problem.

### 2018-01-26 paper/conclusion.tex
Update conclusion and appendix

Despite the complexity of the neural network, DeepPicar uses a
low-cost Raspberry Pi 3 quad-core computer as its sole computing
resource. We systematically analyzed the real-time characteristics of
the Pi 3 platform in the context of deep-learning based real-time
control appilcations, with a special emphasis on real-time deep neural
network inferencing.
We also evaluated other, more powerful, embedded computing
platforms to better understand achievable real-time performance of
DeepPicar's deep-learning based control system and the impact of
computing hardware architectures.
We find all tested embedded platforms, including the Pi 3, are capable
of supporting deep-learning based real-time control, from 20 Hz up to
100 Hz, depending on the platform and its system
configuration. However, shared resource contention remains an
important issue that must be considered in applying deep-learning
models on shared memory based embedded computing platforms.

>>>>

Despite the complexity of the neural network, DeepPicar uses a
low-cost Raspberry Pi 3 quad-core computer as its sole computing
resource. We systematically analyzed the real-time characteristics of
the Pi 3 platform in the context of deep-learning based real-time
control applications, with a special emphasis on real-time deep neural
network inferencing.
We also evaluated other, more powerful, embedded computing
platforms to better understand achievable real-time performance of
DeepPicar's deep-learning based control system and the impact of
computing hardware architectures.
We find all tested embedded platforms, including the Pi 3, are capable
of supporting deep-learning based real-time control, from 20 Hz up to
100 Hz, depending on the platform and its system
configuration. However, shared resource contention remains an
important issue that must be considered in applying deep-learning
models on shared memory based embedded computing platforms.
